On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-01-04 pps-linear-bound/J220-AJC-review-reply-1.tex

%\usepackage[backend=biber,style=gost-numeric,sorting=nyt]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}

\begin{document}

Dear Editor and Referees,

Thank you for your attention paid to the paper.
I've done my best to cover all the remarks and advices,
and the present document is a detailed description of the improvements done.

First of all, I'd like to say special thanks to Referee 2 for the advice
to better guide the reader through the long list of technical auxiliary results.
As it was recommended, I've performed a major revision:
the structure of the paper has been rearranged.
Section 2 has been split into 3 smaller sections;
moreover, each section of main part has been divided into subsections
(see last paragraphs of Introduction for detailed description).

Due to such a rearrangement, numbers of most Lemmas, Theorems etc. have been changed,
and many results have been permuted to fit the new structure.
Thus, it is rather impossible to mention the page and line numbers of every change that has been made,
as it had been requested by the Editor.
As a possible solution, I've published all the workflow at my GitHub:
\\
https://github.com/nickkolok/sct-statya/commits/master
\\
As far as I put all my work on the topic into the single repository,
I've marked the commits concerning this paper with ``[J220]''.

@@

		Yes, it was.
		The comment has been added before the proposition (which is now Proposition 3.5).

	\item

		> Please add a proof for Proposition 2.12.

		Thank you ver much for this remark.
		I have to admit that the result is not formulated correctly.
		The edits affect Definition 2.2 (ex Definition 2.11), Proposition 2.3 (ex Proposition 2.12) and Lemma 2.4 (ex Lemma 2.13).
		Proposition 2.3 now has a self-contained proof.

### 2020-01-11 pps-linear-bound/J220-AJC-review-reply-1.tex

%\usepackage[backend=biber,style=gost-numeric,sorting=nyt]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}

\begin{document}

Dear Editor and Referees,

Thank you for your attention paid to the paper.
I've done my best to incorporate all the remarks and advices,
and the present document is a detailed description of the improvements done.

@@

		Fixed. Page 1, line -7.

	\item

		> As the author’s recent preprint
		``On diameter bounds for planar integral point sets in semi-general position''
		is not very long and overlaps the content of the present paper,
		it might be a good idea to summarize both to a single paper.

		This is the only remark for which I have to write a rebuttal,
		and the reason is that
		the paper ``On diameter bounds for planar integral point sets in semi-general position''
		has already been submitted to another journal.
		Thus, it seems to be impossible to include its content into the present paper.
		Moreover, if the referees insist, I can
		\textbf{
		try to split the present paper into two ones:
		}
		one about the lower bound and one about integral point sets with distance 1.
		The present paper looks rather long, and the requested proofs (see below)
		have made it even more longer.
		However, if the paper will be published as a single one, then I'll also be very glad.

@@

		Yes, it was.
		The comment has been added before the proposition (which is now Proposition 3.5).

	\item

		> Please add a proof for Proposition 2.12.

		Thank you ver much for this remark.
		I have to admit that the result was not formulated correctly.
		The edits affect Definition 2.2 (ex Definition 2.11), Proposition 2.3 (ex Proposition 2.12) and Lemma 2.4 (ex Lemma 2.13).
		Proposition 2.3 now has a self-contained proof.

@@

		> The “blow up” procedure needs an explanation – not everybody is an expert on this.

		Construction 5.10 now provides the explanation.

\end{enumerate}

Minor remarks have been implemented precisely as they had been suggested.
As for minor remark 3, a brief proof for the corresponding Proposition 3.6 has been added.

### 2020-02-21 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Make the reference list even more cute
[J220] Second round of remarks

\usepackage[backend=biber,style=gost-numeric,sorting=nyt]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

@@

Sections 2--4 are devoted to the linear lower bound.
Each Section consists of 2 Subsections: General results an Special results.
In General results, avoid attempts to provide tight estimates;
such attempts are done in Special results.

@@

However, Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}
do not seem to show the way for improving the bound
due to the following well-known theorem,
which can be proved by an application of inversion~\cite{solymosi2010question}.
\begin{theorem}
	\label{thm:rational_set_on_circle}
	There exists a dense subset $P$ of the unit circle such that for any $P_1, P_2 \in P$
	the distance $|P_1 P_2|$ is rational.
\end{theorem}
We conjecture that thorough investigation of existing examples of circular integral point sets
~\cite{bat2018number,harborth1993upper,piepmeyer1996maximum}
will lead to the negative answers for the
Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}.

>>>>

\usepackage[backend=biber,bibstyle=ieee,citestyle=numeric,sorting=nyt]{biblatex}
\DeclareFieldFormat{sentencecase}{#1}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}

@@

Sections 2--4 are devoted to the linear lower bound.
Each Section consists of 2 Subsections: General results and Special results.
In General results, we do not aim to provide tight estimates;
they are discussed in Special results.

@@

However, Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}
do not seem to show the way for improving the bound
due to the following well-known theorem,
which can be proved by an application of circle inversion~\cite{solymosi2010question}.
\begin{theorem}
	\label{thm:rational_set_on_circle}
	There exists a dense subset $P$ of the unit circle such that for any $P_1, P_2 \in P$
	the distance $|P_1 P_2|$ is rational.
\end{theorem}
We conjecture that thorough investigation of existing examples of circular integral point sets
~\cite{bat2018number,harborth1993upper,piepmeyer1996maximum}
will lead to the negative answers for the
Problems~\ref{prb:square_side_length_and_diameter_power} and~\ref{prb:square_side_length_and_diameter_linear}.
